Reproducibility in Plant Pathology

### 2018-06-09 README.rmd
Update static docs

# Reproducibility.in.Plant.Pathology

@@

> Sparks, A.H., Del Ponte, E.M., Everhart, S., Foster, Z., Grünwald, N. (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>

@@

> Sparks, A.H., Del Ponte, E.M., Everhart, S., Foster, Z.S.L., Grünwald, N., (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Status and Best Practices for Reproducible Research In Plant Pathology'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.1250665>

>>>>

# Reproducibility in Plant Pathology

@@

> Del Ponte, E.M., Everhart, S., Foster, Z., Grünwald, N., Sparks, A.H. (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>

@@

> Del Ponte, E.M., Everhart, S., Foster, Z.S.L., Grünwald, N., Sparks, A.H. (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Status and Best Practices for Reproducible Research In Plant Pathology'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.1250665>
